Laws for Creating Trust in the Blockchain Age

### 2017-09-18 tex/article.tex
Added Raynor as co-author

  \author*[1]{Johan Pouwelse}
  \author[2]{André de Kok}
  \author[3]{Joost Fleuren}
  \author[4]{Peter Hoogendoorn}
  \author[5]{Martijn de Vos}
  \runningauthor{Pouwelse, de Kok, Fleuren, Hoogendoorn and de Vos}
  \affil[1]{Department of Software Technology, Delft University of Technology}
  \affil[2]{National Service for Identity Data, Netherlands}
  \affil[3]{Chamber of Commerce, Netherlands}
  \affil[4]{ABN AMRO}
  \affil[5]{Department of Software Technology, Delft University of Technology}
  %\affil[4]{Chamber of Commerce}
  \title{Laws for Creating Trust in the Blockchain Age}
  \abstract{Humanity's notion of trust is shaped by new platforms operating in the emerging sharing economy, acting as intermediate matchmaker for ride sharing, housing facilities or freelance labour, effectively creating an environment where strangers trust each other. While millions of people worldwide rely on online sharing activities, such services are often facilitated by a few predatory companies, managing trust relations. This centralization of responsibility raises questions about ethical and political issues like regulatory compliance, data portability and monopolistic behaviour. Recently, blockchain technology has gathered a significant amount of support and adoption, due to its inherent decentralized and tamper-proof structure.\\We present a blockchain-powered blueprint for a shared and public \emph{programmable economy}. The focus of our architecture is on four essential primitives: digital identities, blockchain-based trust, programmable money and marketplaces. Trust is established using only historical interactions between strangers to estimate trustworthiness. Every component of our proposed technology stack is designed according to the defining principles of the Internet itself: self-governance, autonomy and shared ownership. Real-world viability of each component is demonstrated with a functional prototype or running code. Our vision is that the highlighted technology stack devises trust, new acts, principles and rules beyond the possibilities in current economic, legal and political systems.}
  \keywords{Blockchain, Trust, Programmable Economy, Transactions}

>>>>

  \author*[1]{Johan Pouwelse}
  \author[2]{André de Kok}
  \author[3]{Joost Fleuren}
  \author[4]{Peter Hoogendoorn}
  \author[5]{Raynor Vliegendhart}
  \author[6]{Martijn de Vos}
  \runningauthor{Pouwelse, de Kok, Fleuren, Hoogendoorn, Vliegendhart and Vos}
  \affil[1]{Department of Software Technology, Delft University of Technology}
  \affil[2]{National Service for Identity Data, Netherlands}
  \affil[3]{Chamber of Commerce, Netherlands}
  \affil[4]{ABN AMRO}
  \affil[5]{The Netherlands’ Cadastre, Land Registry and Mapping Agency}
  \affil[6]{Department of Software Technology, Delft University of Technology}
  %\affil[4]{Chamber of Commerce}
  \title{Laws for Creating Trust in the Blockchain Age}
  \abstract{Humanity's notion of trust is shaped by new platforms operating in the emerging sharing economy, acting as intermediate matchmaker for ride sharing, housing facilities or freelance labour, effectively creating an environment where strangers trust each other. While millions of people worldwide rely on online sharing activities, such services are often facilitated by a few predatory companies, managing trust relations. This centralization of responsibility raises questions about ethical and political issues like regulatory compliance, data portability and monopolistic behaviour. Recently, blockchain technology has gathered a significant amount of support and adoption, due to its inherent decentralized and tamper-proof structure.\\We present a blockchain-powered blueprint for a shared and public \emph{programmable economy}. The focus of our architecture is on four essential primitives: digital identities, blockchain-based trust, programmable money and marketplaces. Trust is established using only historical interactions between strangers to estimate trustworthiness. Every component of our proposed technology stack is designed according to the defining principles of the Internet itself: self-governance, autonomy and shared ownership. Real-world viability of each component is demonstrated with a functional prototype or running code. Our vision is that the highlighted technology stack devises trust, new acts, principles and rules beyond the possibilities in current economic, legal and political systems.}
  \keywords{Blockchain, Trust, Programmable Economy, Transactions}
